\documentclass[sigconf]{acmart}
\usepackage{booktabs} % For formal tables
\usepackage{multirow}
\usepackage{color}
\usepackage{subfigure} % Written by Steven Douglas Cochran
\usepackage{array}
\usepackage{breqn}
\usepackage{{inputenc}}
\usepackage{balance}
\usepackage{multirow,tabularx}
\usepackage{longtable}
\usepackage{booktabs,longtable}
\usepackage{hhline}
\usepackage[flushleft]{threeparttable}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{thmtools}
\usepackage{enumitem}
\usepackage{verbatim}
\usepackage{amsfonts}
\usepackage{hyperref}
\hypersetup{colorlinks=false,linkcolor=blue,urlcolor=blue,citecolor=red}
\epstopdfsetup{update}

\newcommand\norm[1]{\left\lVert#1\right\rVert}
\newcommand{\Lapl}{\mathbf{\mathop{\mathcal{L}}}}
\newcommand{\Trans}[1]{{#1}^{\top}}
\newcommand{\Trace}[1]{tr\left({#1}\right)}
\newcommand{\Bracs}[1]{\left({#1}\right)}
\newcommand{\Mat}[1]{\mathbf{#1}}
\newcommand{\MatS}[3]{\mathbf{#1}^{#2}_{#3}}
\newcommand{\Space}[1]{\mathbb{#1}}
\newcommand{\Set}[1]{\mathcal{#1}}
\newcommand{\vectornorm}[1]{\left|\left|#1\right|\right|}
\newcommand{\bpi}{\boldsymbol{\pi}}
\newcommand{\BlockMat}[2]{\left[\begin{matrix}#1\\#2\end{matrix}\right]}
\newcommand{\BlockMatSquare}[4]{\left[\begin{matrix}#1 & #2\\#3 & #4\end{matrix}\right]}

\newcommand{\ie}{\emph{i.e., }}
\newcommand{\eg}{\emph{e.g., }}
\newcommand{\etal}{\emph{et al.}}
\newcommand{\st}{\emph{s.t. }}
\newcommand{\etc}{\emph{etc.}}
\newcommand{\wrt}{\emph{w.r.t. }}
\newcommand{\cf}{\emph{cf. }}
\newcommand{\aka}{\emph{aka. }}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]


\hyphenpenalty=10000
\tolerance=5000


% defining the \BibTeX command - from Oren Patashnik's original BibTeX documentation.
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\copyrightyear{2020} \acmYear{2020} \setcopyright{acmlicensed}\acmConference[SIGIR '20]{Proceedings of the 43rd International ACM SIGIR Conference on Research and Development in Information Retrieval}{July 25--30, 2020}{Virtual Event, China} \acmBooktitle{Proceedings of the 43rd International ACM SIGIR Conference on Research and Development in Information Retrieval (SIGIR '20), July 25--30, 2020, Virtual Event, China} \acmPrice{15.00} \acmDOI{10.1145/3397271.3401063} \acmISBN{978-1-4503-8016-4/20/07}

\begin{document}
\fancyhead{}

\title{LightGCN: Simplifying and Powering Graph Convolution Network for Recommendation}
%\title{Lightening Graph Convolution Network for Recommendation}

\author{Xiangnan He}
\affiliation{
\institution{University of Science and Technology of China}
}\email{xiangnanhe@gmail.com}

\author{Kuan Deng}
\affiliation{
\institution{University of Science and Technology of China}
}\email{dengkuan@mail.ustc.edu.cn}



\author{Xiang Wang}
\affiliation{
\institution{National University of Singapore}
}\email{xiangwang@u.nus.edu}
%\renewcommand{\shortauthors}{Xiang \etal}

\author{Yan Li}
\affiliation{
\institution{Beijing Kuaishou Technology \\Co., Ltd.}
}\email{liyan@kuaishou.com}

\author{Yongdong Zhang}
\affiliation{
\institution{University of Science and Technology of China}
}\email{zhyd73@ustc.edu.cn}

\author{Meng Wang}
\authornote{Meng Wang is the corresponding author.}
\affiliation{
\institution{Hefei University of Technology}
}\email{eric.mengwang@gmail.com
}



\setcounter{page}{1}
\pagenumbering{Roman}

\begin{abstract}
Graph Convolution Network (GCN) has become new state-of-the-art for collaborative filtering. Nevertheless, the reasons of its effectiveness for recommendation are not well understood. 
Existing work that adapts GCN to recommendation lacks thorough ablation analyses on GCN, which is originally designed for graph classification tasks and equipped with many neural network operations. 
However, we empirically find that the two most common designs in GCNs --- feature transformation and nonlinear activation --- contribute little to the performance of collaborative filtering. Even worse, including them adds to the difficulty of training and degrades recommendation performance. 

In this work, we aim to simplify the design of GCN to make it more concise and appropriate for recommendation. We propose a new model named LightGCN, including only the most essential component in GCN --- neighborhood aggregation --- for collaborative filtering. Specifically, LightGCN learns user and item embeddings by linearly propagating them on the user-item interaction graph, and uses the weighted sum of the embeddings learned at all layers as the final embedding. 
Such simple, linear, and neat model is much easier to implement and train, exhibiting substantial improvements (about 16.0\% relative improvement on average) over Neural Graph Collaborative Filtering (NGCF) --- a state-of-the-art GCN-based recommender model --- under exactly the same experimental setting. Further analyses are provided towards the rationality of the simple LightGCN from both analytical and empirical perspectives. Our implementations are available in both TensorFlow\footnote{\url{https://github.com/kuandeng/LightGCN}} and PyTorch\footnote{\url{https://github.com/gusye1234/pytorch-light-gcn}}. 
%Further experiments reveal that ...
%Codes will be released upon acceptance. 

%We conduct empirical comparison with Neural Graph Collaborative Filtering (NGCF) --- a state-of-the-art GCN-based recommender model --- under the same experimental setting. 
%While this simple linear model exhibits better accuracy than existing nonlinear GCN-based recommenders, the setting of the weight of each layer affects its effectiveness much. To avoid manually tuning the setting on a new dataset, we further propose to learn them based on the validation set, automating the usage of the simplified GCN model. 
%Extensive experiments on three real-world datasets demonstrate the effectiveness of our simple and neat . 
\end{abstract}
%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
	<ccs2012>
	<concept>
	<concept_id>10002951.10003317.10003347.10003350</concept_id>
	<concept_desc>Information systems~Recommender systems</concept_desc> <concept_significance>500</concept_significance>
	</concept>
	</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Information systems~Recommender systems}
\vspace{-5pt}
\keywords{Collaborative Filtering, Recommendation, Embedding Propagation, Graph Neural Network}
\maketitle


\input{1_introduction}
\input{2_preliminary}
\input{3_method_new}
\input{4_experiment}
\input{5_related}
\input{6_conclusion}


\bibliographystyle{ACM-Reference-Format}
\balance

\bibliography{ms}
\balance
\scriptsize

\end{document}
